\documentclass{article}
\usepackage{amsmath} % equation, align, matrix, *, &, \\, \left, \right
\usepackage{graphicx} % figure
\usepackage{subcaption} % subfigure
\usepackage{comment} % To comment
\usepackage{hyperref} % To hyperlink and ref
\usepackage{enumitem} % To list
\usepackage[utf8]{inputenc}
\usepackage{wrapfig}
\usepackage{ulem}
\usepackage[backend=bibtex,style=numeric]{biblatex}
\usepackage{subfiles} %multifile latex projects
\usepackage{multirow}
\usepackage{booktabs}

\graphicspath{{images/}{../images/}}

\bibliography{lib} 

\title{Idea de proyecto}
\author{Tim Reiprich \\ Tegshigzugder Otgonbayar \\ Maltagliati Luca}


\begin{document}
\maketitle
%\section{}
%\subsection{}
%\subsubsection{}

%\paragraph{}
%\subparagraph{}

\pagestyle{plain}
\pagenumbering{gobble} %hide page numbers

\paragraph*{Project: Height / capacity monitor}\mbox{}\\

\begin{comment}

Using an ultrasonic sensor or similar, monitor the height of a water tank, paper stack, garbage container, or similar. Think of multiple sensors to map the height in different positions of the container or different containers. To properly manage the filling / emptying of the container, monitoring the tank capacity, etc. Local warning by LEDs, minimum / maximum level alarms, etc.

The context and general description of the device to be designed
Basic scheme of system hardware (components and what information they exchange)
Summary of system operation
List of things you have to do to carry out the project, identifying what you know how to do and what you don't. 
Possible extensions

\end{comment}

\section{Context and general description of the device}

Our project focuses on the measurement of containers holding some kind of
liquid. Based on the volume of these containers alarms can be sent to the users
to notify them about the amount. To accomplish this, sensors will be used, that
can determine if the height of the volume is above or below a certain
threshold. \par

\subsection{Hardware scheme}

The basic scheme of system hardware is described as follows: the main components
are the micro-controller as central server, the sensors and a web-page. The
sensors must be able to connect to the servers by a WiFi-connection and for this
we assume that the connection is robust and will be available in the given
environment.  \par

\subsection{Sensor}
We will use an ultrasonic sensor to measure the level of the liquid. \\
A good example could be the sensor \textit{Ultrasonic Sensor Module HC-SR-04 by
  Robokart}. We chose this approach because it is one of the best ways to sense
proximity and detect levels with high reliability. \\ 

Every sensor is connected to a micro-controller that collects the data and sends
them to the central server via WiFi. \\ 

Every container will have a micro-controller connected to one or more sensors.
Certain specified heights of minimal and maximal volumes will be set, depending
on various factors, like the position of the container, the probability of it to
be used, the type of liquid filled in and others.

\subsection{Central server}

We suppose the existence of a LAN network to which controllers and central
server are connected. This lets the micro-controllers communicate with the
central server, sending it continuously the measurements of the liquid
heights. \\

The central server will perform control on the thresholds and, in case of need,
will send an alert to the user. \\ 

The central server could also host a web-page (for example developed with
Node-RED framework) in which all the data are visualized in diagrams in a
user-friendly interface, to let it be usable also by non-technical people. \\


\section{Steps of the project}

The first steps of the project will be to research about similar projects and
identifying platforms, programming languages and frameworks, choosing
the most suitable ones for our case.
Furthermore, the connection between devices
plays a crucial role, so we need to know what kind of protocols are needed. \par

Possible extensions are to also give specific numbers of the height of the
containers, how much volume they contain. \\

It is also possible to set up LEDs; their light will warn about specific
situations, e.g. when a container is empty a green light is shown, a red one when
is full.

\begin{comment}

\maketitle
\newpage

\pagenumbering{arabic} %show page numbers in arabic
\tableofcontents % from the section headings
\newpage

\listoffigures
 
\listoftables

%\listoftables
\newpage

\subfile{einleitung/einleitung}
\newpage

\subfile{grundlagen/grundlagen}
\newpage

\subfile{analyse/analyse}
\newpage

\printbibliography

\subfile{entwicklung/entwicklung}
\newpage

\subfile{evaluation/evaluation}
\newpage

\subfile{zusammenfassungundausblick/zusammenfassungundausblick}
\newpage

\end{comment}

\end{document}